\documentclass{book}

\begin{document}

\chapter*{References}
\begin{enumerate}
	
	\item http://www.mmsonline.com/articles/a-new-milling-101-what-milling-is-then-and-now-plus-a-glossary-of-milling-terms 
	\item http://www.mmsonline.com/articles/a-new-milling-101-what-milling-is-then-and-now-plus-a-glossary-of-milling-terms 
	\item http://www.sickinsight-online.com/safety-and-more-sick-provides-protection-and-navigation-data-for-kukas-kmr-iiwa/ 
	\item http://medicaldesign.com/contract-manufacturing/modern-cnc-machining-prescription-product-development 
   	\item http://articles.sae.org/11272/ 
	\item https://en.wikipedia.org/wiki/Multiaxis\_machining 
	\item https://en.wikipedia.org/wiki/Milling\_(machining) 
	\item http://www.engineersrule.com/motion-studies-and-how-to-do-them/

	\item http://help.solidworks.com/2017/English/SolidWorks/cworks/c\_Study\_Types.htm 
	\item SolidWorks forums
	\item Dimensions manual 
	\item Specification manual
	\item https://robotics.stackexchange.com/questions/10256/dynamic-torque-simulation-for-a-6-dof-robotic-arm
	\item Handbook of Industrial Robotics, Volume 1, edited by Shimon Y. Nof. 
	\item KUKA manual “01-Mastering and unmastering”
	\item KUKA manual “07-KSS\_82\_Software programming\_en”
	\item KUKA manual “KST\_WorkVisual\_en”
	\item KUKA manual “KUKA.Sim\_2.2\_Installation\_en”
	\item KUKA manuals “KST\_GripperSpotTech\_32\_en”
	\item http://blog.robotiq.com/bid/72815/Top-5-Applications-for-Robotic-Electric-Grippers 
	\item https://www.kuka.com/en-de/products/robot-systems/software/application-software/kuka\_gripper\_spottech 
	\item https://www.robot-forum.com/robotforum/kuka-robot-forum/valves-and-inputs-on-the-wrist-krc4-agilus-kr6-r900-sixx-17168/ 
\item https://www.aliexpress.com/item/0-3kw-Air-cooled-spindle-ER11-chuck-CNC-300W-Spindle-Motor-Power-Supply-speed-governor-Clamp/32698980494.html?spm=2114.search0304.4.109.YTDqf4 
	\item https://www.repetier.com/repetier-g-code-plugin-for-inskscape/
	\item http://javakuka.com/xyzabc/
	\item KST Expert Programming Manual KSS 5.2
	\item INTRODUCING ROBOTICS: MAKING ROBOTS MOVE QUEENSLAND UNIVERSITY OF TECHNOLOGY
	\item Robotics, Vision and Control: Fundamental Algorithms in MATLAB. Book by Peter Corke
	\item Shigley’s Mechanical Engineering Design, Richard G. Budynas, J. Keith Nisbett, 10th edition, 2014.
	\item KR AGILUS six with W \& C variants Specifications.
	 
	\item http://wiki.ros.org/ROS/Introduction
	\item A Gentle Introduction to ROS, Jason M. O’Kane
	\item Learning ROS for Robotics Programming, Aaron Martinez ,Enrique Fernández.
	\item OpenNI user Guide.
	\item https://rosresearch.wordpress.com/2013/12/26/openni-nite-skeleton-tracking-algorithm-related-notes/
	\item http://pr.cs.cornell.edu/humanactivities/data/NITE.pdf
	\item http://wordpress.mrreid.org/2011/08/20/kinect-physics/
	\item http://sourceforge.net/projects/openshowvar/
	\item https://github.com/aauc-mechlab/jopenshowvar/
	\item http://filipposanfilippo.inspitivity.com/publications/jopenshowvar-an-open-source-cross-platform-communication-interface-to-kuka-robots.pdf          
	\item https://www.robodk.com/forum/attachment.php?aid=4
	\item http://answers.ros.org/question/30575/detecting-user-position-with-kinect-without-psi-pose/ 
	\item KSS KUKA Robot Programming 1 Training -KSS8\_v4.
	\item KST-Expert\_Programming\_manual KSS 5.2.
	\item Notes\_ Bochum KUKA Programming.
	\item KRL Quickguide Syntax 8x.
	\item 07-KSS\_82\_Software programming.
	\item KST\_GripperSpotTech\_32.
	\item Spez\_KR\_AGILUS\_sixx\_CR.
	\item http://javakuka.com/xyzabc
	\item www.globalrobots.com
	
	
	
	
	
	
		
\end{enumerate}


\end{document}
